Notes on Validated Model Counting \\ Version of \today

### 2022-04-24 doc/dd/c3-eval.tex
Added and revised examples

\begin{tikzpicture}
\definecolor{neutralcolor}{RGB}{0,0,0}
\definecolor{pathcolor}{RGB}{0,0,0}
\definecolor{fillcolor}{RGB}{255,255,255}
\definecolor{background}{RGB}{225,225,225}
\definecolor{highcolor}{RGB}{0,0,0}
\definecolor{lowcolor}{RGB}{0,0,0}
\draw (1.32,6.80) [thin,neutralcolor] -- (0.26,5.74);
\draw (1.32,6.80) [thin,neutralcolor] -- (1.68,5.03);
\draw (1.68,5.03) [thin,neutralcolor] -- (2.74,3.97);
\draw (1.68,5.03) [thin,neutralcolor] -- (1.32,3.27);
\draw (1.32,3.27) [thin,neutralcolor] -- (0.26,2.21);
\draw (1.32,3.27) [thin,neutralcolor] -- (1.68,1.50);
\draw (1.68,1.50) [thin,neutralcolor] -- (2.74,0.44);
\draw (1.68,1.50) [thin,neutralcolor] -- (0.62,0.44);
\draw [thin,fill=fillcolor,draw=fillcolor] (1.68,5.03) circle [radius=0.26];
\node at (1.68,5.03) {{\texttt{*}}};
\draw [thin,fill=fillcolor,draw=fillcolor] (1.68,1.50) circle [radius=0.26];
\node at (1.68,1.50) {{\texttt{*}}};
\draw [thin,fill=fillcolor,draw=fillcolor] (2.74,0.44) circle [radius=0.44];
\node at (2.74,0.44) {$1-w_2$};
\draw [thin,fill=fillcolor,draw=fillcolor] (1.32,6.80) circle [radius=0.26];
\node at (1.32,6.80) {{\texttt{+}}};
\draw [thin,fill=fillcolor,draw=fillcolor] (1.32,3.27) circle [radius=0.26];
\node at (1.32,3.27) {{\texttt{+}}};
\draw [thin,fill=fillcolor,draw=fillcolor] (2.74,3.97) circle [radius=0.44];
\node at (2.74,3.97) {$1-w_1$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.26,2.21) circle [radius=0.26];
\node at (0.26,2.21) {$w_2$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.62,0.44) circle [radius=0.26];
\node at (0.62,0.44) {$w_3$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.26,5.74) circle [radius=0.26];
\node at (0.26,5.74) {$w_1$};
\node [right] at (1.59,6.80) {$s_7$};
\node [left] at (1.41,5.03) {$p_6$};
\node [right] at (1.59,3.27) {$s_5$};
\node [left] at (1.41,1.50) {$p_4$};
\end{tikzpicture}%%

>>>>

\begin{tikzpicture}
\definecolor{neutralcolor}{RGB}{0,0,0}
\definecolor{pathcolor}{RGB}{0,0,0}
\definecolor{fillcolor}{RGB}{255,255,255}
\definecolor{background}{RGB}{225,225,225}
\definecolor{highcolor}{RGB}{0,0,0}
\definecolor{lowcolor}{RGB}{0,0,0}
\draw (2.12,8.74) [thin,neutralcolor] -- (2.12,7.41);
\draw (2.12,7.41) [thin,neutralcolor] -- (0.35,4.77);
\draw (2.12,7.41) [thin,neutralcolor] -- (2.12,5.65);
\draw (2.12,5.65) [thin,neutralcolor] -- (0.35,4.77);
\draw [fill=neutralcolor,draw=neutralcolor] (1.24,5.21) circle [radius=0.09];
\draw (2.12,5.65) [thin,neutralcolor] -- (2.12,3.88);
\draw (2.12,3.88) [thin,neutralcolor] -- (0.35,1.24);
\draw (2.12,3.88) [thin,neutralcolor] -- (2.12,2.12);
\draw (2.12,2.12) [thin,neutralcolor] -- (0.35,1.24);
\draw [fill=neutralcolor,draw=neutralcolor] (1.24,1.68) circle [radius=0.09];
\draw (2.12,2.12) [thin,neutralcolor] -- (2.12,0.35);
\draw (0.35,4.77) [thin,neutralcolor] -- (0.35,3.88);
\draw (0.35,1.24) [thin,neutralcolor] -- (0.35,0.35);
\draw [thin,fill=neutralcolor,draw=neutralcolor] (0.35,4.77) circle [radius=0.00];
\node at (0.35,4.77) {};
\draw [thin,fill=fillcolor,draw=neutralcolor] (1.24,5.21) circle [radius=0.26];
\node at (1.24,5.21) {$\sim$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (1.24,1.68) circle [radius=0.26];
\node at (1.24,1.68) {$\sim$};
\draw [thin,fill=neutralcolor,draw=neutralcolor] (0.35,1.24) circle [radius=0.00];
\node at (0.35,1.24) {};
\draw [thin,fill=fillcolor,draw=neutralcolor] (2.12,5.65) circle [radius=0.44];
\node at (2.12,5.65) {$\times$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (2.12,2.12) circle [radius=0.44];
\node at (2.12,2.12) {$\times$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (2.12,7.41) circle [radius=0.44];
\node at (2.12,7.41) {$+$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (2.12,3.88) circle [radius=0.44];
\node at (2.12,3.88) {$+$};
\draw [thin,fill=fillcolor,draw=fillcolor] (2.12,8.74) circle [radius=0.35];
\node at (2.12,8.74) {$\sigma(\phi_1)$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.35,0.35) circle [radius=0.35];
\node at (0.35,0.35) {$w_2$};
\draw [thin,fill=fillcolor,draw=fillcolor] (2.12,0.35) circle [radius=0.35];
\node at (2.12,0.35) {$w_3$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.35,3.88) circle [radius=0.35];
\node at (0.35,3.88) {$w_1$};
\node [right] at (2.56,7.41) {$s_7$};
\node [right] at (2.56,5.65) {$p_6$};
\node [right] at (2.56,3.88) {$s_5$};
\node [right] at (2.56,2.12) {$p_4$};
\end{tikzpicture}%%

### 2022-04-24 doc/dd/c3.tex
New example
Added and revised examples

\begin{tikzpicture}
\definecolor{neutralcolor}{RGB}{0,0,0}
\definecolor{pathcolor}{RGB}{0,0,0}
\definecolor{fillcolor}{RGB}{255,255,255}
\definecolor{background}{RGB}{225,225,225}
\definecolor{highcolor}{RGB}{0,0,0}
\definecolor{lowcolor}{RGB}{0,0,0}
\draw (1.32,6.62) [thin,neutralcolor] -- (0.26,5.56);
\draw (1.32,6.62) [thin,neutralcolor] -- (1.68,4.85);
\draw (1.68,4.85) [thin,neutralcolor] -- (2.74,3.79);
\draw (1.68,4.85) [thin,neutralcolor] -- (1.32,3.09);
\draw (1.32,3.09) [thin,neutralcolor] -- (0.26,2.03);
\draw (1.32,3.09) [thin,neutralcolor] -- (1.68,1.32);
\draw (1.68,1.32) [thin,neutralcolor] -- (2.74,0.26);
\draw (1.68,1.32) [thin,neutralcolor] -- (0.62,0.26);
\draw [thin,fill=fillcolor,draw=neutralcolor] (1.68,4.85) circle [radius=0.53];
\node at (1.68,4.85) {$\mathbin{\land_{\textrm{pv}}}$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (1.68,1.32) circle [radius=0.53];
\node at (1.68,1.32) {$\mathbin{\land_{\textrm{pv}}}$};
\draw [thin,fill=fillcolor,draw=fillcolor] (2.74,0.26) circle [radius=0.26];
\node at (2.74,0.26) {$\overline{x}_2$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (0.79,6.09) rectangle (1.85,7.15);
\node at (1.32,6.62) {$\mathbin{\lor_{\textrm{pa}}}$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (0.79,2.56) rectangle (1.85,3.62);
\node at (1.32,3.09) {$\mathbin{\lor_{\textrm{pa}}}$};
\draw [thin,fill=fillcolor,draw=fillcolor] (2.74,3.79) circle [radius=0.26];
\node at (2.74,3.79) {$\overline{x}_1$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.26,2.03) circle [radius=0.26];
\node at (0.26,2.03) {$x_2$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.62,0.26) circle [radius=0.26];
\node at (0.62,0.26) {$x_3$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.26,5.56) circle [radius=0.26];
\node at (0.26,5.56) {$x_1$};
\node [right] at (1.85,6.62) {$s_7$};
\node [left] at (1.15,4.85) {$p_6$};
\node [right] at (1.85,3.09) {$s_5$};
\node [left] at (1.15,1.32) {$p_4$};
\end{tikzpicture}%%

>>>>

\begin{tikzpicture}
\definecolor{neutralcolor}{RGB}{0,0,0}
\definecolor{pathcolor}{RGB}{0,0,0}
\definecolor{fillcolor}{RGB}{255,255,255}
\definecolor{background}{RGB}{225,225,225}
\definecolor{highcolor}{RGB}{0,0,0}
\definecolor{lowcolor}{RGB}{0,0,0}
\draw (2.12,8.74) [thin,neutralcolor] -- (2.12,7.41);
\draw (2.12,7.41) [thin,neutralcolor] -- (0.35,4.77);
\draw (2.12,7.41) [thin,neutralcolor] -- (2.12,5.65);
\draw (2.12,5.65) [thin,neutralcolor] -- (0.35,4.77);
\draw [fill=neutralcolor,draw=neutralcolor] (1.24,5.21) circle [radius=0.09];
\draw (2.12,5.65) [thin,neutralcolor] -- (2.12,3.88);
\draw (2.12,3.88) [thin,neutralcolor] -- (0.35,1.24);
\draw (2.12,3.88) [thin,neutralcolor] -- (2.12,2.12);
\draw (2.12,2.12) [thin,neutralcolor] -- (0.35,1.24);
\draw [fill=neutralcolor,draw=neutralcolor] (1.24,1.68) circle [radius=0.09];
\draw (2.12,2.12) [thin,neutralcolor] -- (2.12,0.35);
\draw (0.35,4.77) [thin,neutralcolor] -- (0.35,3.88);
\draw (0.35,1.24) [thin,neutralcolor] -- (0.35,0.35);
\draw [thin,fill=neutralcolor,draw=neutralcolor] (0.35,4.77) circle [radius=0.00];
\node at (0.35,4.77) {};
\draw [thin,fill=neutralcolor,draw=neutralcolor] (0.35,1.24) circle [radius=0.00];
\node at (0.35,1.24) {};
\draw [thin,fill=fillcolor,draw=neutralcolor] (2.12,5.65) circle [radius=0.44];
\node at (2.12,5.65) {$\mathbin{\land_{\textrm{v}}}$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (2.12,2.12) circle [radius=0.44];
\node at (2.12,2.12) {$\mathbin{\land_{\textrm{v}}}$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (2.12,7.41) circle [radius=0.44];
\node at (2.12,7.41) {$\mathbin{\lor_{\textrm{a}}}$};
\draw [thin,fill=fillcolor,draw=neutralcolor] (2.12,3.88) circle [radius=0.44];
\node at (2.12,3.88) {$\mathbin{\lor_{\textrm{a}}}$};
\draw [thin,fill=fillcolor,draw=fillcolor] (2.12,8.74) circle [radius=0.35];
\node at (2.12,8.74) {$t_1$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.35,0.35) circle [radius=0.35];
\node at (0.35,0.35) {$x_2$};
\draw [thin,fill=fillcolor,draw=fillcolor] (2.12,0.35) circle [radius=0.35];
\node at (2.12,0.35) {$x_3$};
\draw [thin,fill=fillcolor,draw=fillcolor] (0.35,3.88) circle [radius=0.35];
\node at (0.35,3.88) {$x_1$};
\node [right] at (2.56,7.41) {$s_7$};
\node [right] at (2.56,5.65) {$p_6$};
\node [right] at (2.56,3.88) {$s_5$};
\node [right] at (2.56,2.12) {$p_4$};
\end{tikzpicture}%%

### 2022-04-24 doc/mc-notes.tex
Added and revised examples

For assignment $\interp$ and a Boolean formula $E$ over $X$, we
use the notation $\interp\subs{x_i}{E}$ to denote the assignment
$\interp'$, such that $\interp'(x_j) = \interp(x_j)$ for all $j \not = i$
and $\interp'(x_i) = \interp(E)$, where $\interp(E)$ is the value obtained by evaluating formula $E$ with each variable assigned the value given by $\interp$.
In particular, the notation
$\interp(\subs{x_i}{\obar{x}_i})$
indicates the assignment in which the value
assigned to $x_i$ is complemented, while others remain unchanged.

@@

\begin{figure}
  \centering{
    \begin{minipage}{0.4\textwidth}
      A) Schema   \\[2ex]
    \centering{\input{dd/c3}}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
    B) Cost Computation\\[2ex]
    \centering{\input{dd/c3-eval}}
    \end{minipage}
  }
\caption{Schema for Formula $x_1 \lor x_2 \lor x_3$ and its Cost Computation}
\label{fig:c3:schema}
\end{figure}

@@

@@

    {\tt 2} & {\tt i}   & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
            & {\tt p}   & {\tt 4 -2 3}  &            & & Declare $p_4 = \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 3} & {\tt ab}  & {\tt 4 2 3 0} & {\tt 0}    & & Defining clauses for $p_4$ \\
    {\tt 4} & {\tt ab}  & {\tt -4 -2 0} & {\tt -2 0}    & & \\
    {\tt 5} & {\tt ab}  & {\tt -4 -3 0} & {\tt -2 0}    & & \\
            & {\tt p}   & {\tt 5 -1 4}  &             & & Declare $p_5 = \obar{x}_1 \pand p_4 = \obar{x}_1 \pand \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 6} & {\tt ab}  & {\tt 5 1 -4 0} & {\tt 0}    & & Defining clauses for $p_5$ \\
    {\tt 7} & {\tt ab}  & {\tt -5 -1 0} & {\tt -6 0}    & & \\
    {\tt 8} & {\tt ab}  & {\tt -5 4 0} & {\tt -6 0}    & & \\
    {\tt 9} & {\tt ar}  & {\tt -5 0} & {\tt 7 8 4 5 1 0} & & Assert $t_1 = \obar{p}_5 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dr}  & {\tt 1 } & {\tt 3 6 7 0} & & Delete clause $C_1$\\
            & {\tt p}   & {\tt 6 1 -2} &              & & Declare $p_6 = x_1 \pand \obar{x}_2$ \\    
    {\tt 10} & {\tt ab}  & {\tt 6 -1 2 0}  & {\tt 0}    & & Defining clauses for $p_6$ \\ 
    {\tt 11} & {\tt ab}  & {\tt -6 1 0}    & {\tt -10 0} & & \\
    {\tt 12} & {\tt ab}  & {\tt -6 -2 0}    & {\tt -10 0} & & \\ 
    {\tt 13} & {\tt ar} & {\tt -6 0} & {\tt 11 12 2 0}  & & Assert $t_2 = \obar{p}_6 = \obar{x}_1 \lor x_2$ \\
            & {\tt dr}  & {\tt 2 } & {\tt 10 13 0} & & Delete clause $C_2$\\
            & {\tt s}   & {\tt 7 5 6}   & {\tt 7 11 0}  & & Declare $s_7 = \obar{t}_1 \por \obar{t}_2$ \\
    {\tt 14} & {\tt ab}  & {\tt -7 5 6 0}  & {\tt 0}    & & Defining clauses for $s_7$ \\ 
    {\tt 15} & {\tt ab}  & {\tt  7 -5 0}    & {\tt -5 0} &  \\  
    {\tt 16} & {\tt ab}  & {\tt  7 -6 0}    & {\tt -5 0} & &  \\
    {\tt 17} & {\tt ar}  & {\tt -7 0}       & {\tt 9 13 0} & & Assert $t_3 = \obar{s}_7 = t_1 \land t_2$ \\
             & {\tt dr}  & {\tt 9}          & {\tt 15 17 0} & & Delete $t_1$\\
             & {\tt dr}  & {\tt 13}         & {\tt 16 17 0} & & Delete $t_2$\\
  \end{tabular}
}  
  \caption{CRAT Proof Steps for Formula $(x_1 \lor x_2 \lor x_3) \land (\obar{x}_1 \lor x_2$}
  \label{fig:p2:crat}
\end{figure}

>>>>

For assignment $\interp$ and a Boolean formula $\phi$ over $X$, we
use the notation $\interp\subs{x_i}{\phi}$ to denote the assignment
$\interp'$, such that $\interp'(x_j) = \interp(x_j)$ for all $j \not = i$
and $\interp'(x_i) = \interp(\phi)$, where $\interp(\phi)$ is the value obtained by evaluating formula $E$ with each variable assigned the value given by $\interp$.
In particular, the notation
$\interp(\subs{x_i}{\obar{x}_i})$
indicates the assignment in which the value
assigned to $x_i$ is complemented, while others remain unchanged.

@@

\begin{figure}
  \centering{
    \begin{minipage}{0.4\textwidth}
      A) Schema   \\[2ex]
    \centering{\input{dd/c3}}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
    B) Cost Computation\\[2ex]
    \centering{\input{dd/c3-eval}}
    \end{minipage}
  }
\caption{Schema for Formula $\phi_1 = x_1 \lor x_2 \lor x_3$ and its Cost Computation}
\label{fig:c3:schema}
\end{figure}

@@

\begin{figure}
  \centering{
    \begin{minipage}{0.4\textwidth}
      A) Schema   \\[2ex]
    \centering{\input{dd/p2}}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
    B) Cost Computation\\[2ex]
    \centering{\input{dd/p2-eval}}
    \end{minipage}
  }
\caption{Schema for Formula $\phi_2 = (x_1 \lor x_2 \lor x_3) \land (\obar{x}_1 \lor x_2)$ and its Cost Computation}
\label{fig:c3:schema}
\end{figure}

@@

    {\tt 2} & {\tt i}   & {\tt -1 2 0}  &            & & Input clause $C_2$ \\
            & {\tt p}   & {\tt 4 -2 3}  &            & & Declare $p_4 = \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 3} & {\tt ab}  & {\tt 4 2 3 0} & {\tt 0}    & & Defining clauses for $p_4$ \\
    {\tt 4} & {\tt ab}  & {\tt -4 -2 0} & {\tt -2 0}    & & \\
    {\tt 5} & {\tt ab}  & {\tt -4 -3 0} & {\tt -2 0}    & & \\
            & {\tt p}   & {\tt 5 -1 4}  &             & & Declare $p_5 = \obar{x}_1 \pand p_4 = \obar{x}_1 \pand \obar{x}_2 \pand \obar{x}_3$ \\
    {\tt 6} & {\tt ab}  & {\tt 5 1 -4 0} & {\tt 0}    & & Defining clauses for $p_5$ \\
    {\tt 7} & {\tt ab}  & {\tt -5 -1 0} & {\tt -6 0}    & & \\
    {\tt 8} & {\tt ab}  & {\tt -5 4 0} & {\tt -6 0}    & & \\
    {\tt 9} & {\tt ar}  & {\tt -5 0} & {\tt 7 8 4 5 1 0} & & Assert $t_1 = \obar{p}_5 = x_1 \lor x_2 \lor x_3$ \\
            & {\tt dr}  & {\tt 1 } & {\tt 3 6 7 0} & & Delete clause $C_1$\\
            & {\tt p}   & {\tt 6 1 -2} &              & & Declare $p_6 = x_1 \pand \obar{x}_2$ \\    
    {\tt 10} & {\tt ab}  & {\tt 6 -1 2 0}  & {\tt 0}    & & Defining clauses for $p_6$ \\ 
    {\tt 11} & {\tt ab}  & {\tt -6 1 0}    & {\tt -10 0} & & \\
    {\tt 12} & {\tt ab}  & {\tt -6 -2 0}    & {\tt -10 0} & & \\ 
    {\tt 13} & {\tt ar} & {\tt -6 0} & {\tt 11 12 2 0}  & & Assert $t_2 = \obar{p}_6 = \obar{x}_1 \lor x_2$ \\
            & {\tt dr}  & {\tt 2 } & {\tt 10 13 0} & & Delete clause $C_2$\\
            & {\tt s}   & {\tt 7 5 6}   & {\tt 7 11 0}  & & Declare $s_7 = \obar{t}_1 \por \obar{t}_2$ \\
    {\tt 14} & {\tt ab}  & {\tt -7 5 6 0}  & {\tt 0}    & & Defining clauses for $s_7$ \\ 
    {\tt 15} & {\tt ab}  & {\tt  7 -5 0}    & {\tt -5 0} &  \\  
    {\tt 16} & {\tt ab}  & {\tt  7 -6 0}    & {\tt -5 0} & &  \\
    {\tt 17} & {\tt ar}  & {\tt -7 0}       & {\tt 9 13 0} & & Assert $t_3 = \obar{s}_7 = t_1 \land t_2$ \\
             & {\tt dr}  & {\tt 9}          & {\tt 15 17 0} & & Delete $t_1$\\
             & {\tt dr}  & {\tt 13}         & {\tt 16 17 0} & & Delete $t_2$\\
  \end{tabular}
}  
  \caption{CRAT Proof Steps for Formula $\phi = (x_1 \lor x_2 \lor x_3) \land (\obar{x}_1 \lor x_2)$}
  \label{fig:p2:crat}
\end{figure}
